A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-07-05 papers/earths-future/submission.tex
Klaus edits

Many critical infrastructure services around the world are aging \cite<\eg,>{ho_dams:2017}.
Moreover, anticipated changes to regulation, economics and finance, patterns of population and infrastructure use, and climate challenge their ability to meet their design objectives \cite{doss-gollin_txtreme:2021,doss-gollin_fatalism:2020,chester_reliable:2020}.
The need to upgrade and expand infrastructure motivates the question: for which possible futures should infrastructure systems and components be designed?
The answer to this question depends in part on values: intrinsic trade-offs between safety, performance, cost, and other objectives depend on context and stakeholder preferences \cite{keller_management:2021} and are often regulated by statute or industry guidelines \cite{bruneau_multihazard:2017}.
For example, hospitals and critical infrastructure are generally designed to a higher standard of risk protection than ordinary buildings \cite{asce_7-10:2013}.
At the same time, performance depends upon future conditions, and so decisions about which scenario to design for are necessarily subject to implicit or explicit assumptions about the likelihood or possibility of different futures.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{tradeoffs-by-rcp}
  \caption{
    Each probabilistic model or scenario leads to a different estimate of the Pareto frontier.
    For emphasis, we highlight three representative models: the Brick Slow model \protect\cite{wong_brick0.2:2017} under \gls{rcp} 2.6, the K14 \protect\cite{kopp_probabilistic:2014} model under \gls{rcp} 6.0 and the DP16 model \protect\cite{deconto_antarctica:2016,kopp_evolving:2017} under \gls{rcp} 8.5.
    (A): trade-off between up-front cost (which is a monotonic function of height increase) and expected lifetime costs.
    (B): trade-off between up-front cost and lifetime expected damages (eq.~\ref{eq:led}).
    Light gray lines show estimates for all 16 models (four \gls{rcp} scenarios times four physical parameterizations) considered.
    Colored lines highlight three representative models for emphasis.
    Gray lines and the smiling face in the lower left corner indicate the direction of preference.
  }\label{fig:tradeoffs-by-rcp}
\end{figure}

@@

This approach is, in a sense, another form of exploratory modeling: instead of considering a very large ensemble of \glspl{sow}, we consider a much smaller set of probabilistic models.
This approach is attractive because it allows modelers to focus on their domain expertise (\eg, the response of ice sheets and global sea levels to a particular climate future).
However, conditioning simulations on a set of climate futures and physical models presents what we term ``the multiple \gls{pdf} problem'' because it leaves decision makers with many \glspl{pdf} to choose from and hence many trade-off curves to navigate.
The multiple \gls{pdf} problem has also been shown in other contexts.
For example, \citeA{sharma_rcp:2021} model the reliability of stormwater infrastructure under different climate models and downscaling methods, finding diverging estimates of future rainfall hazard, even under a single \gls{rcp} scenario.
Similarly, \citeA{wong_nola:2017} construct 18 probability distribution functions for future flood risk in New Orleans, considering multiple models for ice sheet dynamics and storm surge and multiple \gls{rcp} scenarios and \citeA{haasnoot_sealevelrise:2021} identify global adaptation needs for different scenarios of \gls{slr}.
Although this scenario-conditional analysis is appropriate for understanding differences between models, its key limitation is that it \textbf{places the burden for deciding which model to design for onto the end user.}

>>>>

Many critical infrastructure services around the world are aging \cite<\eg,>{ho_dams:2017}.
Moreover, changes in regulations, finance, patterns of population and infrastructure use, and the climate system challenge the ability of critical infrastructures to meet design objectives \cite{doss-gollin_txtreme:2021,doss-gollin_fatalism:2020,chester_reliable:2020}.
The need to upgrade and expand infrastructure motivates the question: for which possible futures should infrastructure systems and components be designed?
The answer to this question depends in part on values: intrinsic trade-offs between safety, performance, cost, and other objectives depend on context and stakeholder preferences \cite{keller_management:2021} and are often regulated by statute or industry guidelines \cite{bruneau_multihazard:2017}.
For example, hospitals and critical infrastructure are generally designed to a higher standard of risk protection than ordinary buildings \cite{asce_7-10:2013}.
At the same time, performance depends upon future conditions, and so decisions about which scenario to design for are necessarily subject to implicit or explicit assumptions about the likelihood or possibility of different futures.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{tradeoffs-by-rcp}
  \caption{
    Each probabilistic model or scenario leads to a different estimate of the Pareto frontier.
    For emphasis, we highlight three representative models: the Brick Slow model \protect\cite{wong_brick0.2:2017} under \gls{rcp} 2.6, the K14 \protect\cite{kopp_probabilistic:2014} model under \gls{rcp} 6.0 and the DP16 model \protect\cite{deconto_antarctica:2016,kopp_evolving:2017} under \gls{rcp} 8.5.
    (A): trade-off between up-front cost (which is a monotonic function of height increase) and expected lifetime costs.
    (B): trade-off between up-front cost and lifetime expected damages (eq.~\ref{eq:led}).
    Light gray lines show estimates for all 16 models (four \gls{rcp} scenarios times four physical parameterizations) considered.
    Colored lines highlight three representative models for emphasis.
    The gray arrows indicate the direction of preference.  
  }\label{fig:tradeoffs-by-rcp}
\end{figure}

@@

This approach is, in a sense, another form of exploratory modeling: instead of considering a very large ensemble of \glspl{sow}, we consider a much smaller set of probabilistic models.
This approach is attractive because it allows modelers to focus on their domain expertise (\eg, the response of ice sheets and global sea levels to a particular climate future).
However, conditioning simulations on a set of climate futures and physical models presents what we term ``the multiple \gls{pdf} problem'' because it leaves decision makers with many \glspl{pdf} to choose from and hence many trade-off curves to navigate.
The multiple \gls{pdf} problem has also been shown in other contexts.
For example, \citeA{sharma_rcp:2021} model the reliability of stormwater infrastructure under different climate models and downscaling methods, finding diverging estimates of future rainfall hazard, even under a single \gls{rcp} scenario.
Similarly, \citeA{wong_nola:2017} construct 18 probability distribution functions for future flood risk in New Orleans, considering multiple models for ice sheet dynamics and storm surge and multiple \gls{rcp} scenarios. As a last example, \citeA{haasnoot_sealevelrise:2021} identify global adaptation needs for different \gls{slr} scenarios.
Although this scenario-conditional analysis is appropriate for understanding differences between models, its key limitation is that it \textbf{places the burden for deciding which model to design for onto the end user.}
